---
title: "movie"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
movies <- read.csv(file='/Users/professorserrano/Documents/College/Fall 2020 Semester/Stats in R/archive/movies_metadata.csv') 
```

Here are the top 10 languages in the dataset and a same graph of vote_average by revenue, colored by language: 

```{r top languages}
lang <- movies %>%
  group_by(original_language) %>%
  count %>%
  arrange(desc(n))

top_10_lang <- unique(lang$original_language[1:10])

top_langs <- lang %>%
  filter(original_language %in% top_10_lang) %>%
  mutate(percentage = n / 45466)

```

Here's a filter for just the English movies, with a little test graph plotting vote_average by revenue: 

```{r english movies}

en_movies <- movies %>%
  filter(original_language == "en") 

en_movies

ggplot(en_movies,mapping=aes(vote_average,revenue)) +
  geom_point() +
  labs(title = "English Movies")
```

Here's a filter for all movies not in English, with the same test graph: 

```{r not english}
not_english <- lang %>%
  filter(original_language != "en")

not_english

ggplot(not_english,mapping=aes(original_language,n)) +
  geom_point() +
  coord_flip() +
  labs(title="Not English movies")
```

This gives the breakdown by genre, and then the breakdown of dramas by original language. 
The trouble with genre is that they're kind of additive - there's often multiple genres at once. So if something's a Romance and a Comedy, I think it would be double-counted using the str_detect. 

```{r genres}
genres <-  movies %>%
  group_by(genres) %>%
  count %>%
  arrange(desc(n)) 
genres

dramas <- movies %>%
  filter(stringr::str_detect(genres, "Drama")) %>%
  group_by(original_language) %>%
  count %>%
  arrange(desc(n)) %>%
  mutate(percentage = n / 20265)
dramas
```

This gives the breakdown by studio. 

```{r studios}
studios <- movies %>%
  group_by(production_companies) %>%
  count %>%
  arrange(desc(n)) %>%
studios


```


